---
title: "Belgium airports"
author: "Stefaan Delanghe"
date: "10/20/2016"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plyr)
```

## Case study

We will map all the airports in Belgium. This means outside of large we take into account the smaller ones, heliport and closed airports.

### Gathering
The data set has been retrieved from [HDX](https://data.humdata.org/dataset/ourairports-bel). For which we thank them to make this case study possible.

Here follows a list of what we will do with the data.

- download the airports from Belgium.
- clean and tidy up the data.
- plot the airports on a ploty graph.

## Metadata

|                    |                                               |
|--------------------|-----------------------------------------------|
| Source             | OurAirports.com community web site            |
| Contributor        | OurAirports                                   |
| Date of dataset    |                                               |
| Location           | Belgium                                       |
| Visibility         | Public                                        |
| License            | Public domain                                 |
| Methodology        | Other                                         |
| Caveats / Comments | Unverified live data. May change at any time. |


## Download data
### Here we download the file from HDX website.
```{r download, echo = TRUE, cache=TRUE}
download.file("http://ourairports.com/countries/BE/airports.hxl", 
              destfile = "be-airports.csv")
```

### Now we clean and tidy up the data
```{r tidy, echo = TRUE}
airports <- read.csv("be-airports.csv", header = T)
airportNames <- c("longitude_deg", "latitude_deg", "name")
col.num <- which(colnames(airports) %in% airportNames)
airportMarkers <- data.frame(airports[,col.num])
airportMarkers <- airportMarkers[-1,]
airportMarkers <- rename(airportMarkers, 
        c("latitude_deg"="lat", "longitude_deg"="lng", "name"="popup"))
```
airportMarkers contains the data for belgium airports and will be used to plot.

## Map airports in Belgium
Here you can find a map with all the airports (large, small, heliport and closed).
```{r plot, echo = FALSE,message=FALSE}
library(leaflet)

airportMarkers %>% leaflet() %>%
      addProviderTiles("Esri.WorldImagery") %>%
      addMarkers() %>%
      setView(lat=50.901401519800004, lng=4.48443984985, zoom=7)
```
